Economic Evaluation of Mis-speficied Geographically Weighted Regression Models for Site-specific Nitrogen Management

### 2023-07-17 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd

---
output:
  html_document: default
---
# Reply to the Reviewer #2

@@

Your comments are in blue, and our responses are in black.

First, we would like to express our sincere gratitude for the reviewer's careful examination and critique of our manuscript. The insightful comments and suggestions have significantly contributed to the paper's clarity, detail, and overall strength.  In return, we have attempted to carefully address each of the comments and revise the manuscript in response.

<span style = "color: blue;">This study examines the economic value associated with three statistical methods used to generate site-specific nitrogen application rates: 1) geographically weighted regressions using the method of Rakshit et al. (2020) denoted as GWR-R, 2) geographically weighted regressions using the method of Trevisan et al. (2021) denoted as GWR-T, and 3) shape-constrained additive models (SCAM). Using straightforward Monte Carlo simulations, the two GWR methods are used to determine the economically optimal nitrogen rate (EONR) and profits from variable rate applications (VRA), while the SCAM methodology is used to determine the EONRs and profits for uniform rate applications (URA). These rates are based on estimations of site-specific corn yield functions for six cells across 1,440 subplots. The authors find the GWR-T outperforms GWR-R when the nitrogen price (relative to corn) is low, but GWR-R outperforms GWR-T when the nitrogen price is relatively high. This is because of the relative over- and underestimation of the EONRs. The study also finds that both GWR-T and GWR-R may have substantially overestimated the economic value of VRA; the net benefit of VRA over URA is much smaller, roughly $2 per acre (just over $5 per hectare, on average). For convenience, my review below is organized into a set of general comments, specific comments, and comments related to the exposition and writing, with each being arranged in order of page number. All comments are designed to strengthen the research.</span>

@@

<br>

## <span style = "color: blue;">General Comments</span>

<span style = "color: blue;">To some extent, this research is related to studies that examine the "value" of forecasting models by assessing their measure of inaccuracy. Given that determining the value of general regression methodologies is not overly common in the relevant literature here, why not add 1-2 paragraphs that ties your study to other studies that measure the "value" of certain econometric techniques?
</span>

Very good point. What makes this study differ from previous studies is that the model "value" is not measured by the accuracy of parameter estimates, but rather by the ultimate economic return. We have followed your suggestion above by expanding our review of previous studies to highlight what our research adds to the literature.  Please see in particular section 2.3 of the revised manuscript.

<span style = "color: blue;">One of the most important questions in the literature relates to how variable rate technologies (VRT) can reduce negative externalities like fertilizer and chemical runoff and leaching. Clearly, this is not the research objective, and addressing a much more burning question in the literature would involve additional terms in the equation on p. 10, line 294 that represent the negative environmental externalities. The authors should clarify early on that "economically optimal" means "privately optimal" rather than "socially optimal."</span>

Thank you for the suggestion.   We have explicitly stated the following at the end of the Introduction section of the revised manuscript: *"While the environmental impacts of fertilizer management are of great social importance, for simplicity we confine our analysis to its private economic impacts."*

<span style = "color: blue;">It strikes me as odd that, even with a minor clause on line 207 of p. 10, there is no real discussion of the corn price or nitrogen price in the methods section. What are the summary statistics and/or assumptions about p and w? What is the underlying intuition regarding the dependence of the relative performance of GWRR/GWRT to the corn-to-nitrogen price ratio (though this is partially explained in the paragraph on pages 15-16)? Any intuition about the ratios of 4.2, 5.4, and 10.4?</span>

Good point. We have included a brief discussion of the historical corn and nitrogen prices in the first paragraph of the Results section, which is section 5.  Additionally, we have included Appendix I: Historical Corn and Nitrogen Prices in the supplementary material to provide a more detailed description of the collection, calculation, and summary statistics of the historical price data. We also apologize for the typos of the price ratios 4.16, 5.44 and 10.35 in the previous version of the manuscript. The correct price ratios 5.44, 6.56, and 7.67 are used in the revised manuscript. The intuition underlying the dependence of the relative performances of GWRR and GWRT to the nitrogen-corn price ratio was explained in the paragraphs on pages 15-16 of the original manuscript, and that discussion has been included in the revised manuscript.  The main difference arises from the models' specifications of the coefficient on $N^2$.  The GWRR model allows for varying coefficient on $N^2$, leading to a wider range of estimated EONRs, while the GWRT model restricts the coefficient on $N^2$ to be constant, leading to a narrower range of estimated EONRs.  When nitrogen is expensive relative to corn, the true range of EONRs should be larger, and therefore the economic penalty of GWRR's over-estimation of EONR range will be smaller.  When the nitrogen-corn price ratio is lower, the true EONR range will be smaller, and GWRT's under-estimation of the EONR range is less of an issue. At the reviewer's request, we will be happy to further enhance the manuscript's discussion of this topic.

<span style = "color: blue;">Where is there no in-text reference to, or explanation of, Figure 4? I do not know what to make of this lone figure.</span>

We apologize for the confusion. That figure was meant to compare the estimated and true GWR coefficients $\beta_1$ and $\beta_2$.  But since we have already compared the estimated and true EONR's in another figure, so the figure 4 was redundant. We have removed it from the revised manuscript.

@@

<br>

## <span style = "color: blue;">Specific Comments</span>

<span style = "color: blue;">P. 1, line 23: Site-specific farming, these days, does not have to be very precise, although the early literature conflated precision ag and site-specific farming. More importantly, VRT is just one component of precision ag; they are not synonymous.</span>

Reply: We agree with the reviewer's comment that precision agriculture, site-specific farming, and variable-rate technology are not synonymous. Although in the literature those terms are often used interchangeably, they are not strictly speaking equivalent. We removed the statement in the parentheses "also known as site-specific farming, or variable-rate technology" to avoid misleading the audiences.

<span style = "color: blue;">P. 5, lines 89-90: By this point, it would have been useful to add 1-2 sentences or a footnote about parallels with nonparametric estimators. Using multiple data points to derive local estimates, as in kernel density estimation, is nothing new. It would be helpful to provide more background on this. More broadly, at this point, besides the economics, why should we care about GWR relative to other spatial statistics methods?</span>

We agree with the reviewer's comment that GWR is only one of many nonparametric estimators of local yield responses.  But our research goal was not to compare GWR with other estimators, nor to advocate the use of GWR.  We have tried to make this much more clear in the Introduction of the revised manuscript.  We explain as background that the GWR model has gained attention in developing site-specific input recommendations due to its minimal requirement of costly field characteristics data. We explain that our intent is to further test the value of having GWR available as a tool for the analysis of on-farm precision experimentation data and consequential input management recommendations. We do not intend to involve other spatial statistics methods in the current paper. But we do plan to conduct similar simulation-based economic evaluations of other local response estimation methods (such as the spatial kriging smoothing) in future research.

<span style = "color: blue;">P. 9, line 192: Here, do you mean that you set the 1370 kg ha-1 to be the square root of the sill variances?</span>

Thanks for pointing out the typo. Yes, it should be the square root of the sill variances since 1379 kg ha−1 was the mean of the standard deviations. We have corrected that typo in the revised manuscript at (page x, line xx in the revised manuscript).

<span style = "color: blue;">P. 11, line 220: At the first mention of shape-constrained additive models (SCAM), there should be a few sentences of explanation, either in the body or as a footnote. Even after the partial explanation on lines 232-233, it is still somewhat unclear and warrants more detail. The general readers of JAAEA are likely to not know, either.</span>

Thank you for the suggestion. In section 4.5.1 of the revised manuscript we have expanded our explanation of SCAM to clarify that it is a regression model that can fit a more flexible and non-linear response relationship and also allows for shape constraints that can incorporate prior knowledge or theories.

<span style = "color: blue;">Pp. 11-12, lines 238-245: To check, l=K, i.e., the total number of splines from the equation on line 238 equals the total number of splines used for f ̂_SCAM (∙)? If so, use the same notation.</span>

Yes, the $l$ and $k$ should have been the same. We use $k$ in the revised manuscript.

<span style = "color: blue;">P. 13, lines 268-270: How robust are the N^*_{GWR-T,j} rates to variations in the AIC-chosen bandwidth parameters? More information about this needs to be provided.</span>

Reply: If we understand the question correctly, you are asking about the robustness of GWR estimates to bandwidth selection. Choosing bandwidth is indeed a crucial step in GWR estimation, and there are many different bandwidth selection methods in the literature. In this study we used the corrected version of AIC approach [@fotheringham2017multiscale; @lu2017geographically] to determine the optimal bandwidth. It is a commonly used approach in practice, and also the same approach used by @rakshit2020 and @trevisan2021spatial which can make our simulation evaluations consistent. Since the corrected AIC method generates a unique bandwidth, we did not conduct any robustness check to bandwidths. We agree the GWR results could vary when choosing different bandwidths, but the choices of other bandwidth values other than the AIC-chosen one may be arbitrary. We added more discussions about bandwidth selection in page x, lines xxx of the revised manuscript.

<span style = "color: blue;">P. 15, lines 303-305: Why are the numbers from these sentences blank? In particular, the median benefit of VRA under GWRR is ? and the median benefit of VRA under GWRT is…?</span>

Our apologies for the typos. We have corrected them and filled in the correct numbers. (See page x, line xx in the revised manuscript.)

<span style = "color: blue;">P. 15: You first discuss figure 6 and then move to figure 5. Put all figures in order.</span>

We have corrected the order of the figures.

@@

<br>

## <span style = "color: blue;">Writing</span>

<span style = "color: blue;">P. 2, line 45: This should be "data are", not "data is". </span>

Corrected.

<span style = "color: blue;">P. 2, line 52: Basically or actually? Vagueness here makes it difficult to assess the degree to which OSU's calculators are being used directly. </span>

We removed the word "basically" in the pertinent part of the revised manuscript.

<span style = "color: blue;">P. 2, line 54: To avoid confusing a general agricultural economics audience, I would use an abbreviation other than Rx for site-specific recommendations. </span>

Reply: In precision agriculture, the site-specific input management recommendation map is commonly called "prescription" or "Rx" by researchers and the industry. While we are certainly willing to defer to the editor's judgment, We have elected to keep this abbreviation in the revised manuscript, but have added a brief explanation of the notation. In the USA, at least, it is widely known that "Rx" means "prescription,"" and it is chiefly used in conversations about medicines and pharmacies.

<span style = "color: blue;">P. 2, lines 49-60: All of these current commercial examples would work better as a footnote as they may become inaccurate in the next 3-10 years (or fewer). </span>

Thank you for the suggestion. We agree that placing the commercial examples in a footnote is a better idea. Please see footnote 1 of the revised manuscript.

<span style = "color: blue;">P. 5, lines 91-114: This page-long paragraph should be split up into at least two paragraphs. The length is taxing. I would consider starting a new paragraph with the sentence beginning on line 97.</span>

We have followed the reviewer's suggestion and broken the discussion into two paragraphs In the revised manuscript.

<span style = "color: blue;">P. 7, line 137: This comment should have been removed by the authors prior to manuscript submission.</span>

Corrected.

<span style = "color: blue;">P. 9, line 189: The acronym DIFM is used before it's spelled out in the sentence, but you should spell it out first and then use the acronym. </span>

The acronym DIFM has been placed after the full name in the revised manuscript.

<span style = "color: blue;">P. 10, line 212: The (j,k) index should be subscripted here.</span>

Thanks for your careful reading. We have subscripted the indices in the revised manuscript where necessary.

<span style = "color: blue;">P. 11, line 221: The second "and" should be "an". </span>

Corrected.

<span style = "color: blue;">P. 11, line 232: Are you using one shape constraint or more than one shape constraint? The language here really matters so as to avoid confusion on the part of the readers.</span>

Here we are modeling a "full-field" response function.  That is, the model assumes that yield response is uniform across the field.  We agree that the language used could cause confusion about whether we were referring to the yield response function or the shape constraint as "single."  We removed the term "single" from the revised manuscript.  Please see section 4.5.1 of the revised manuscript.

<span style = "color: blue;">P. 11, line 235: It seems that 1-2 citations could be added (or are missing) after "well substantiated by agronomic research."</span>

We have cited two additional of agronomic studies to support the statement in section 4.5.1 of the revised manuscript.

<span style = "color: blue;">P. 12, line 253: I know what you mean by the notation f ̂_(GWR-R,j) (N), but the hyphen in the notation almost seems like a subtraction sign. I would recommend changing GWR-R and GWR-T to GWRR and GWRT and then having superscripts here. That is, f ̂_j^GWRR (∙) and f ̂_j^GWRT (∙).</span>

Thank you for the recommendation. We have changed GWR-R and GWR-T GWRR and GWRT throughout the revised manuscript.  We have also put all model names (GWR and SCAM) in superscripts in the pertinent equations.

<span style = "color: blue;">P. 13, line 271: In keeping with your past usage, you should make sure the acronym SCAM is in uppercase throughout the text.</span>

Done. We have put all acronyms in upper case throughout the revised manuscript.

<span style = "color: blue;">P. 15, line 304: "but the its benefit is even negative at when the" should have the typos/redundant wording removed.</span>

Done.

<span style = "color: blue;">P. 17, line 335: Figure 0?</span>

Our apologies for the typo. It should have been Figure 5 and this problem is fixed in our new manuscript.

<span style = "color: blue;">P. 18, line 362: Section title should just be "Discussion". </span>

We have combined what were the two final sections of the original manuscript into one section, headed “Discussion and Conclusions.”

<span style = "color: blue;">P. 34, Figure 8 horizontal axis label: "Estiamated" should be "Estimated". </span>

Corrected.

<span style = "color: blue;">Pp. 19-20, lines 398-400: Can this sentence be sharpened? Right now, it is a bit too vague to be completely useful as a guide to researchers in this area. Specifically, what other statistical estimators should be reconsidered and how (specifically) should they be reassessed?</span>

We have edited the sentence in the revised manuscript, adding detail to explain that other statistical methods commonly used for site-specific yield response estimation literature include regression on field characteristics variables as interaction terms, machine learning, etc. The common assessment approach is to use simulation-based evaluation, much much as we do in our study.

### 2023-07-24 Writing/JAAEA/1stRoundRevision/reply_to_editor.rmd

---
output:
  html_document: default
bibliography: PA.bib
---
# Reply to the editor

Thank you for your thoughtful comments. Addressing them has made our paper much stronger. Below, your comments are in blue, and our responses are in black.

@@

<span style = "color: blue;"> Based on the reviews and your email response, I have decided to give you the opportunity to revise the manuscript and respond to reviewer comments. One major point is that your true DGP assumed a quadratic plateau, but the estimated models use quadratic. This will lead the estimated models to give biased results. In your email response you indicate that you used quadratic plateau as the “true” functional form based on agronomy studies. If the dominant approach in recent literature is to use quadratic functions, then it does seem valuable to quantify the bias from using quadratic rather than quadratic plateau. Please document clearly in the manuscript that quadratic is the common practice (__point 1__). However, the title of your paper is about an economic evaluation of GWR analysis, and the choice of quadratic or quadratic-plateau is not an issue with GWR and this needs to be clear (__point 2__). Also reading through your discussion section, the implications are primarily framed about how GWR performed, but it might completely be an issue with functional form, but the current simulations don't inform us about the source of bias. Ideally, you would compare a GWR model that is quadratic with a GWR model that is quadratic-plateau functional form (__point 3__). </span>

Reply to <span style = "color: blue;"> __point 1__ </span>:

Actually, the dominant functional form used in the literature is quadratic-plateau for <span style = "color: red;"> non-</span>GWR (regualr parametric) regression because a agronomists have come to a consensus  that it better represents the corn-nitrogen relationship. Application of GWR is very new to the field, and no available software packages allow the user to conduct GWR assuming response functions that are non-linear in their parameters at the moment. This technical limitation is the primary reason that both Trevisan et al. (2021) and Rakshit et al. (2020) assumed a quadratic functional form of yield response. We are showing this can be dangerous with GWR, as it is in more traditional regression frameworks. Our paper's message is important--without understanding our evidence and arguments, practitioners or researchers could believe that GWR can provide more than it really can.  One of our conclusions is that it is important for someone to develop a tool in a statistical package that allows application of GWR while modeling yield-input relationships more flexibly.

@@

Reply to <span style = "color: blue;"> __point 2__ </span>:

We fully agree with this point. We are assuming that readers know that the yield-nitrogen relationship is better represented by the quadaratic-plateau.  We make this point explicitly in the revised manuscript, and it is an implicit motivator throughout the manuscript. But, following your responses to us, we have made significant modifications to the manuscript to show clearly that the problem is not with GWR itself, but rather is caused by the technical limitation of their being no GWR package that can handle functional forms that are nonlinear in their coefficients.

@@

Reply to <span style = "color: blue;"> __point 3__ </span>:

This was a real problem in the writing of the original manuscript, and we apologize. As we have written above, our objective is not to reveal any weakness inherent to GWR, but rather to point out that problems caused when software limitations cause the researcher to misspecify the functional form of the yield response function.  But we agree fully that it is interesting to see how GWR performs when the assumed functional form in regression and true functional form in the data generating processes are the same. However, please note that quadratic-plateu is a non-linear model and GWR still cannot be readily used to estimate non-linear yield response.

<span style = "color: blue;"> Revierw #1's other major critique is that the “true” data generation process (DGP) of the parameters does not correspond with a GWR. For example, reviewer #1 argues that the spatial distribution of parameters described in the original manuscript's lines 173-193 does not correspond with a GWR DGP. Is there evidence from the agronomy literature that the DGP (aside from the functional form assumption) follows the process that you specify? Or alternatively, is there evidence from the agronomy literature that the DGP does not follow the GWR DGP described by reviewer #1 in comment #5? My guess is that the agronomy literature has little or nothing to say about this (compared to the functional form assumption), but maybe I'm wrong about that. If there is no evidence to support your proposed DGP or the GWR DGP as “true,” then it is difficult to critique GWR for not correctly estimating your proposed DGP (__specific point 1__). In your email response you state “Our choice of true yield response function is deliberate and just as valid as the data generating process Reviewer #1 recommends.” But if the DGP that you used and the DGP recommended by reviewer #1 are equally valid, then why critique GWR for not correctly estimating your DGP? To critique GWR, you need to argue that your DGP is more valid than the GWR DGP (__specific point 2__). Or you can estimate if GWR is robust to alternative, but equally valid, DGPs.

@@

</span>

First, it is important to reiterate that we are not interested in evaluating GWR itself, even though we presented this idea very poorly in the original.  Again, we are interested in evaluating GWR with a quadratic functional form when the true underlying relationship is quadratic-plateau.  We believe that this point alone addresses many of the concerns addressed by both you and Reviewer 1.

Second, while the DGPs may look complicated, close inspection shows that, other than the functional forms assumed, our DGP and Reviewer 1's suggested DGP are not as different as they may first appear. The reviewer suggested the following:

@@

$$
\begin{aligned}
y^* = X(X'W(s)X)^{-1}X'W(s)y + e^*
\end{aligned}
$$

Another way of writing this is simply

$$
\begin{aligned}
y_i = X_i\beta_i + e_i
\end{aligned}
$$

, where $(X'W(s)X)^{-1}X'W(s)y = \beta$. As shown in Leung, Y., Mei, C. L., & Zhang, W. X. (2000),  $\beta_i$ is the coefficient specific to observation $i$. $W(s)$ ensures that $\beta$ are spatially correlated. The choice of $W(s)$ is arbitrary, and and there for it could be fairly called "cheating" to use the same $W(s)$ in the DGP and for the GWR both.  This method gives an unfair advantage to GWR because the researcher cannot know the real $W(s)$.  The situation is much like the one created becauase the researcher does not know the true weight matrix in spatial econometric approaches.  This can only be called the "correct" GWR DGP only when $W(s)$ is known a priori.

In our DGP, we generate spatially correlated parameters (alpha, ... in equation ) for individual $i$. (Reviewer 1 was under the impression that these parameters were not spatially correlated, but indeed they are.) So, aside from the functional form, the only difference in our DGPs is in the spatial pattern of parameters. It is much as if we were are using a $W(s)$ different from in the above equation, which is an arbitrary parameter chosen by the researcher running MC simulations in the first place. In this sense, our DGP is just as "valid" as the GWR DGP.

In fact, we believe that our DGP is $superior$ to the the one suggested by Reviewer 1 because ours is more flexible. The DGP suggested by the Reviewer 1 cannot accommodate non-linear models, while our DGP can use any functional relationship between $Y$ and $X$. This is critical to our study because the DGP <span style = "color: red;"> needs </span> to include the quadratic-plateau functional form to better represent the actual functional relationship exhibited by corn-nitogen response.

You are right that no agronomic studies have examined whether our DGP or Reviewer 1's is superior. But whereas Reviewer 1's DGP has never been applied in the context of precision agriculture, ours has been used in several articles in prominent, peer-reviewed agronomy and precision agriculture journal [@kakimoto2022causal; @li2023economic].  Of course, we are not claiming that our DGP is "correct."  But it is not inferior to the reviewer's DGP, and we have elected to keep it in our study.

We take responsibility for the poor communication in our original manuscript that generated much of Reviewer 1's poor understanding of our study's methods and motivations. Reviewer 1's thought that our principal abjectives were test GWR itself and to test the accuracy in parameter estimation accuracy.  We believe that in the revised manuscript we have made clear that our goal is to examine the economic effects of using GWR under misspecification of the yield response function.

@@

Reply to <span style = "color: blue;"> __specific point 1__ </span>:

When using the GWR DGP, the researcher cannot know the "true" $W(s)$ matrix, and therefore misspecifying the underlying DGP is unavoidable.  It is not possible to use the "correct" DGP, regardless of whether the underlying model is estimated with GWR.  The point of our article is to point out the importance of the functional form assumption when GWR is used.  If we were to follow Reviewer 1's suggestion that we use quadratic functional form as our true yield-nitrogen response, the whole point of the paper whould be lost.

We will not use the GWR DGP process for two reasons. First, as we mentioned, we are not interested in criticizing GWR itself, but GWR with quadratic form when the true yield response function is better represented by quadratic-plateau (we argued why this is important in our replies above). Also, the GWR DGP process suggested by the reviewer is limited to linear-in-parmeter model (like quadratic model). It simply cannot be used for quadratic-plateau.

@@

But, suppose we are interested in evaluating GWR itself. And, also suppose our DGP and the GWR DGP are very different even though they are in reality very similar as argued above. Even then, we can definitely criticize GWR by using our DGP. Nobody knows the true data generating process of OFPE in the real world. If we use the GWR DGP and find out that GWR performs well, then does that mean GWR performs well in the real world? No. It says that GWR performs well if the data generated in OFEP indeed follow GWR DGP, which of course may not be the true DGP in real world. If GWR does not perform well for a single DGP that is just as valid as GWR DGP, then that would mean we need to be careful applying GWR in the real world. This is not to say, GWR is always bad. But, it is enough to warrant researchers and practitioners that GWR <span style = "color: red;"> may </span> fail. If we show that GWR does not work well with "a" valid DGP, then it is enought to warn people about its potential danger.

<span style = "color: blue;"> In general, it is important in your paper to clarify how much of the bias you estimate is due to the functional form assumption versus the assumption about the DGP. Also, you need to more clearly defend the DGP you choose as the “true” DGP or compare results with alternative DGPs. It seems to me that you will need to rethink your simulations so that you can more clearly sort out the sources of bias. </span>

Reply:

It is not our intention in this paper to distinguish and isolate the sources of bias. Our interest is in showing the bias of using GWR with a quadratic functional form of yield response (as does Trevisan,et al. (2021) ) even though the underlying relationship is quadratic-plateau.  Also, please note that functional form is part of DGP and indeed the most important part of a DGP. There is no such thing as isolating the source of bias of a functional form assumption and a DGP assumption.

If our interest were in understanding the problem of GWR estimation inaccuracy, we should have used quadratic-plateau in our GWR estimation so that the functional forms matched. But, this was not our intent, and anyway at this point in time it would be technically too cumbersome since there is no readily available statistical software to implement it. We are criticizing the practice that has been used by researchers that can give a false impression about how valuable GWR is in providing information for variable rate nitrogen application management in the OFPE setting.

### 2023-07-24 Writing/manuscript_gwr.rmd
modifications on replies

**Abstract**: Geographically weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to derive site-specific input rate recommendations from data generated by on-farm precision experimentation (OFPE). However, the current application of GWR in this context assumes quadratic yield response function even though many of the yield-input relationships has been shown to be better represented by the quadratic-plateau functional form. This is due to lack of readily available methods and statistical packages that allow researchers to estimate non-linear model under the GWR framework, including quadratic-plateau. The key objective of this paper is to investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR with quadratic functional form assumption when in reality the true underlying yield-input relationship is quadratic-plateau. We consider two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE. We show that both GWR approaches suffer significant positive bias, which can lead to large over-estimation of the economic value of applying GWR methods. We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise "over-sell" to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management. We encourage the statistical community to extend the current GWR capability by allowing researchers to model yield-input response more flexibly than currently possible.

@@

>>>>

**Abstract**: Geographically weighted regression (GWR) has been presented as a valuable tool for the estimation of site-specific yield response functions used to derive site-specific input rate recommendations from data generated by on-farm precision experimentation (OFPE).  But applications of GWR in this context have assumed a quadratic yield response function, despite a scientific consensus that the yield-input relationships modeled are better represented by the quadratic-plateau functional form. The quadratic assumption has been made because no readily available statistical packages exist for GWR estimation with non-linear functional forms. The key objective of this paper is to investigate whether, when the true functional form of yield response is quadratic-plateau, assuming a quadratic form introduces bias into the GWR estimation of the economic value of site-specific recommendation maps. We consider two sets of functional-form specifications used by recently published studies of site-specific input management that apply GWR to data from OFPE. We show that both GWR approaches suffer significant positive bias, which can lead to large over-estimation of the economic value of applying GWR methods. We conclude that in many circumstances the information gleaned from using GWR may be far less valuable than has been claimed.  We encourage the statistical community to develop tools in software packages providing GWR that allow more flexibility in functional form assumptions.

@@

# Background:  Estimation of Yield-to-input Response Relationships Using OFPE Data
